### 2015-07-02 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: continued to add pictures and content to hose stream report

% Load packages
\usepackage{graphicx}
\usepackage[super]{nth}
\usepackage{placeins}

@@

\subsection{Water Flow Experimental Procedure}
\label{sec:Water_Flow_Procedure}
A variety of experiments were conducted to examine the impact of different hose streams and application methods on air flow inside a structure. All the experiments were conducted in either the East or West Structure; used a monitor or handline with a combination nozzle to flow water in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns in the structure. Experiments that used a monitor to flow water focused on varying the location of water application, while the experiments that used a handline to flow water focused on varying the pattern in which water was applied.

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_29-32}
\caption[East Structure Layout for Tests 29-32]{East Structure layout for Tests 29-32}
\label{fig:test_29-32_setup}
\end{figure}
\FloatBarrier

@@

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_33_34}
\caption[East Structure Layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
\label{fig:test_33_34_setup}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_2nd_Floor}
\caption[West Structure Layout for Tests 16 and 18]{West Structure first floor (top) and second floor (bottom) layouts for Tests 16 and 18. Both double doors and the south side door on the first floor were in the opened position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_1}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_2nd_Floor}
\caption[West Structure Layout for Tests 17 and 19]{West Structure first floor (top) and second floor (bottom) layouts for Tests 17 and 19. Both double doors on the first floor were in the opened position and the south side door on the first floor was in the closed position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/East_handline_C_BC.pdf}
\caption[Straight Stream and Narrow Fog Stream during Tests 31 and 32]{Straight stream (left column) and narrow fog stream (right column) aimed at ceiling of Room C (top row) and Door BC (bottom row) during Tests 31 and 32}
\label{fig:test_31_32_pic}
\end{figure}
\FloatBarrier

@@

%Where was the handline aimed?%
Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1.75" handline. The difference between the two tests was that Test 18 contained the same flow path configuration as Test 16 (Fig.~\ref{fig:flow_path_1}), while Test 19 contained the same flow path configuration as Test 17 (Fig.~\ref{fig:flow_path_2}). Each test began by flowing water in a straight stream pattern and fixed position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Then, water flow stopped, the two doors were closed, and the procedure was repeated three additional times for sweeping, clockwise, and counterclockwise application patterns. This entire procedure was repeated for narrow fog and wide fog streams.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/Test_18}
\caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18. A straight stream pattern is being applied, and the flow path is fully established with the stairway door and the north side, west double door both opened.}
\label{fig:test_18_pic}
\end{figure}
\FloatBarrier

@@

Figures \ref{fig:Test_16_BDP_A10_Avg_All}-\ref{fig:Test_17_BDP_A13_Avg_All} contain plots of the average velocity through the stairwell door and \nth{2} level, north side, west double door, measured by the bi-directional probes in each doorway for the two application locations and three hose stream patterns for Tests 16 and 17.

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations for Tests 16 and 17}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}}
\\
\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\
\midrule
\textit{Straight} & 
%%%%Test 16%%%% 
0.8 $\pm 0.2$ & 0.9 $\pm 0.2$ & 
%%%%Test 17%%%% 
0.7 $\pm 0.1$ & 0.7 $\pm 0.2$
\\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 16%%%% 
1.4 $\pm 0.1$ & 1.0 $\pm 0.1$ & 
%%%%Test 17%%%% 
0.8 $\pm 0.2$ & 0.8 $\pm 0.1 $          
\\	\multicolumn{5}{c}{}	\\
\textit{Wide Fog} 	& 
%%%%Test 16%%%% 
1.2 $\pm 0.1$ & 1.4 $\pm 0.1$ & 
%%%%Test 17%%%% 
0.9 $\pm 0.2$ & 0.7 $\pm 0.2$
\\
\bottomrule
\end{tabular}
\label{table:Tests_16_17_BDP_A10_Avgs}
\end{table}

\begin{table}[!ht]
\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations for Tests 16 and 17}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}}
\\
\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\
\midrule
\textit{Straight} & 
%%%%Test 16%%%% 
2.8 $\pm 0.6$ & 3.1 $\pm 0.5$ & 
%%%%Test 17%%%% 
2.7 $\pm 0.4$ & 2.3 $\pm 0.8$
\\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 16%%%% 
4.4 $\pm 0.3$ & 3.3 $\pm 0.4$ & 
%%%%Test 17%%%% 
2.6 $\pm 0.6$ & 2.7 $\pm 0.6$
\\	\multicolumn{5}{c}{}	\\
\textit{Wide Fog} 	& 
%%%%Test 16%%%% 
3.9 $\pm 0.5$ & 4.4 $\pm 0.3$ & 
%%%%Test 17%%%% 
3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ 
\\ 
\bottomrule
\end{tabular}
\label{table:Tests_16_17_BDP_A13_Avgs}
\end{table}

@@

\appendix

\chapter{Appendix A}

Placeholder

>>>>

% Load packages
\usepackage{graphicx}
\usepackage[super]{nth}
\usepackage{placeins}
\usepackage{units}
\usepackage[percent]{overpic}

@@

\subsection{Water Flow Experimental Procedure}
\label{sec:Water_Flow_Procedure}
A variety of experiments were conducted to examine the impact of different hose streams and application methods on air flow inside a structure. All the experiments were conducted in either the East or West Structure; used a monitor %reference for specs? 2000 LPM (500 GPM)?
or 1 \nicefrac{3}{4}" handline with a combination nozzle (Fig.~\ref{fig:monitor+handline}) to flow water in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns in the structure. Experiments that used a monitor to flow water focused on varying the location of water application, while the experiments that used a handline to flow water focused on varying the pattern in which water was applied.

\begin{figure}[!ht]
\minipage{3in}
\begin{center}
	\includegraphics[width=2.9in]{../Pictures/monitor}
\end{center} 
\endminipage \hfill
\minipage{3in}
\begin{center}
	\includegraphics[width=2.9in]{../Pictures/handline}
\end{center}
\endminipage \hfill
\caption[Monitor and Handline Equipped with Combination Nozzle]{Monitor (left) and 1 \nicefrac{3}{4}" handline (right). Both are equipped with a combination nozzle and were used in the water flow experiments.}
\label{fig:monitor+handline}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\begin{overpic}[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_29-32}
	\put(83,24){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
\end{overpic}
\caption[East Structure Layout for Tests 29-32]{East Structure layout for Tests 29-32}
\label{fig:test_29-32_setup}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\begin{overpic}[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_33_34}
	\put(66,36){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
\end{overpic}
\caption[East Structure Layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
\label{fig:test_33_34_setup}
\end{figure}
\FloatBarrier

@@

@@

\begin{figure}[!ht]
\begin{overpic}[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_1st_Floor}
	\put(81,23){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
\end{overpic}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_2nd_Floor}
\caption[West Structure Layout for Tests 16 and 18]{West Structure first floor (top) and second floor (bottom) layouts for Tests 16 and 18. Both double doors and the south side door on the first floor were in the opened position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_1}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\begin{overpic}[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_1st_Floor}
	\put(81,23){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
\end{overpic}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_2nd_Floor}
\caption[West Structure Layout for Tests 17 and 19]{West Structure first floor (top) and second floor (bottom) layouts for Tests 17 and 19. Both double doors on the first floor were in the opened position and the south side door on the first floor was in the closed position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/East_handline_C_BC.pdf}
\caption[Straight Stream and Narrow Fog Stream during Tests 31 and 32]{Straight stream (left column) and narrow fog stream (right column) aimed at ceiling of Room C (top row) and Door BC (bottom row) during Tests 31 and 32}
\label{fig:test_31_32_pic}
\end{figure}
\clearpage

@@

\begin{figure}[!ht]
\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/SS_Room_B_Test_34}
\\~\\
\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/NF_Room_B_Test_34}
\\~\\
\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/WF_Room_B_Test_34}
\caption[Straight Stream, Narrow Fog Stream, and Wide Fog Stream during Test 34]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at ceiling of Room B during Test 34}
\label{fig:test_34_pic}
\end{figure}
\FloatBarrier

%Where was the handline aimed?%
Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1 \nicefrac{3}{4}" handline. The difference between the two tests was that Test 18 contained the same flow path configuration as Test 16 (Fig.~\ref{fig:flow_path_1}), while Test 19 contained the same flow path configuration as Test 17 (Fig.~\ref{fig:flow_path_2}). Each test began by flowing water in a straight stream pattern and fixed position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Then, water flow stopped, the two doors were closed, and the procedure was repeated three additional times for sweeping, clockwise, and counterclockwise application patterns. This entire procedure was repeated for narrow fog and wide fog streams.

\begin{figure}[!ht]
\includegraphics[width=4.25in]{../Pictures/Test_18}
\caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18. A straight stream pattern is being applied, and the flow path is fully established with the stairway door and the north side, west double door both opened.}
\label{fig:test_18_pic}
\end{figure}
\clearpage

@@

Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} and Fig.~\ref{fig:Test_16_BDP_A13_Avg_All} contain plots of the average velocity measured by the bi-directional probes in the stairwell doorway (A10) and \nth{2} level, north side, west double doorway (A13), respectively, for Test 16. A similar set of plots was generated using data from Test 17 and can be found in Appendix~\ref{sec:additional_figures}.

Notice, the only instances in which significant air movement (average velocity greater than 0.5 m/s) occurs through either doorway is when the flow path is fully established, or when both the stairwell door and the \nth{2} level, north side, west double door are opened. Tables~\ref{table:Tests_16_17_BDP_A10_Avgs} and~\ref{table:Tests_16_17_BDP_A13_Avgs} contain the average air velocity measured by the bi-directional probes at A10 and A13, respectively, when the flow path was completely established for each hose stream pattern and application location for Tests 16 and 17.

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations when the flow path was fully established during Tests 16 and 17}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}}
\\
\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\
\midrule
\textit{Straight} & 
%%%%Test 16%%%% 
0.8 $\pm 0.2$ & 0.9 $\pm 0.2$ & 
%%%%Test 17%%%% 
0.7 $\pm 0.1$ & 0.7 $\pm 0.2$
\\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 16%%%% 
1.4 $\pm 0.1$ & 1.0 $\pm 0.1$ & 
%%%%Test 17%%%% 
0.8 $\pm 0.2$ & 0.8 $\pm 0.1 $          
\\	\multicolumn{5}{c}{}	\\
\textit{Wide Fog} 	& 
%%%%Test 16%%%% 
1.2 $\pm 0.1$ & 1.4 $\pm 0.1$ & 
%%%%Test 17%%%% 
0.9 $\pm 0.2$ & 0.7 $\pm 0.2$
\\
\bottomrule
\end{tabular}
\label{table:Tests_16_17_BDP_A10_Avgs}
\end{table}

\begin{table}[!ht]
\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations when the flow path was fully established during Tests 16 and 17}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}}
\\
\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\
\midrule
\textit{Straight} & 
%%%%Test 16%%%% 
2.8 $\pm 0.6$ & 3.1 $\pm 0.5$ & 
%%%%Test 17%%%% 
2.7 $\pm 0.4$ & 2.3 $\pm 0.8$
\\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 16%%%% 
4.4 $\pm 0.3$ & 3.3 $\pm 0.4$ & 
%%%%Test 17%%%% 
2.6 $\pm 0.6$ & 2.7 $\pm 0.6$
\\	\multicolumn{5}{c}{}	\\
\textit{Wide Fog} 	& 
%%%%Test 16%%%% 
3.9 $\pm 0.5$ & 4.4 $\pm 0.3$ & 
%%%%Test 17%%%% 
3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ 
\\ 
\bottomrule
\end{tabular}
\label{table:Tests_16_17_BDP_A13_Avgs}
\end{table}

@@

\appendix
\chapter{Appendix}
\label{chap:appendix}

\section{Additional Figures}
\label{sec:additional_figures}
